### 2008-09-18 doc/client/client_technical.tex
Info sys mapping documentation

\vspace*{1.5cm}
%%%%---- A list of authors ----
{\centering \large Mattias Ellert\footnote{mattias.ellert@fysast.uu.se} \large \par}
{\centering \large Iv\'{a}n M\'{a}rton\footnote{martoni@niif.hu} \large \par}
{\centering \large Bjarte Mohn\footnote{bjarte.mohn@fysast.uu.se} \large \par}
{\centering \large P\'{e}ter Stef\'{a}n\footnote{stefan@niif.hu} \large \par}
%%%%---- An abstract - if style is article ----
%\begin{abstract}
%The abstract
%\end{abstract}
\end{titlepage}

@@

The {\ExecutionTarget} is the class representation of a computing
resource (queue) capable of executing a grid job. It serves as input
to the {\Broker} which is foreseen to be able to select between
different {\ExecutionTarget}s from different grid flavours without a
priori knowing their difference. The {\ExecutionTarget} class mimics
the glue2 information model (with a flattened structure), and thus a
mapping between attributes from other information systems into the
glue2 format is needed. Appendix XX shows the current mapping for the
production ARC, ARC1 and gLite middlewares.

@@

{\Job} is a generic job class for storing all job related information.
Attributes are derived from the glue2 information model and thus a
mapping is needed for non glue2 compliant grid middlewares. Appendix
XX shows the present mapping schema.

@@

>>>>

\vspace*{1.5cm}
%%%%---- A list of authors ----
{\centering \large Mattias Ellert\footnote{mattias.ellert@fysast.uu.se} \large \par}
{\centering \large Iv\'{a}n M\'{a}rton\footnote{martoni@niif.hu} \large \par}
{\centering \large Bjarte Mohn\footnote{bjarte.mohn@fysast.uu.se} \large \par}
{\centering \large G\'{a}bor R\H{o}czei\footnote{roczei@niif.hu} \large \par}
%%%%---- An abstract - if style is article ----
%\begin{abstract}
%The abstract
%\end{abstract}
\end{titlepage}

@@

The {\ExecutionTarget} is the class representation of a computing
resource (queue) capable of executing a grid job. It serves as input
to the {\Broker} which is foreseen to be able to select between
different {\ExecutionTarget}s from different grid flavours without a
priori knowing their difference. The {\ExecutionTarget} class mimics
the Glue2 information model (with a flattened structure), and thus a
mapping between attributes from other information systems into the
Glue2 format is needed. Appendix \ref{app:ExTarget} shows the current
mapping for the production ARC, ARC1 and gLite middlewares.

@@

{\Job} is a generic job class for storing all job related information.
Attributes are derived from the Glue2 information model and thus a
mapping is needed for non Glue2 compliant grid middlewares. Appendix
\ref{app:job} shows the present mapping schema.

@@

\appendix

\chapter{{\ExecutionTarget}}
\label{app:ExTarget}

\section{Domain and Location attributes}

\subsection*{std::string DomainName}

ARC0: nordugrid-cluster-name \\
CREAM: GlueSiteName

\subsection*{std::string Owner}

ARC0: nordugrid-cluster-owner

\subsection*{std::string Address}

\subsection*{std::string Place}

CREAM: GlueSiteLocation

\subsection*{std::string PostCode}

ARC0: nordugrid-cluster-location

\subsection*{float Latitude}

CREAM: GlueSiteLatitude

\subsection*{float Longitude}

CREAM: GlueSiteLongitude

\section{ComputingService and ComputingEndpoint attributes}

\subsection*{std::string CEID}

\subsection*{std::string CEName}

\subsection*{std::string Capability}

\subsection*{std::string Type}

\subsection*{std::string QualityLevel}

\subsection*{URL url}

ARC0: nordugrid-cluster-contactstring \\
CREAM: GlueCEInfoContactString

\subsection*{std::string Technology}

\subsection*{std::string Interface}

ARC0: ``GridFTP''

\subsection*{std::string InterfaceExtension}

\subsection*{std::string SupportedProfile}

\subsection*{std::string Implementor}

ARC0: ``NorduGrid''

\subsection*{std::string ImplementationName}

ARC0: ``ARC0'' \\
CREAM: GlueCEImplementationName

\subsection*{std::string ImplementationVersion}

ARC0: nordugrid-cluster-middleware \\
CREAM: GlueCEImplementaionVersion

\subsection*{std::string HealthState}

ARC0: nordugrid-queue-status

\subsection*{std::string ServingState}

CREAM: GlueCEStateStatus (GlueVOView $||$ GlueCE)

\subsection*{std::string IssuerCA}

ARC0: nordugrid-cluster-issuerca (nordugrid-cluster-issuerca-hash)

\subsection*{std::list<std::string> TrustedCA}

ARC0: nordugrid-cluster-trustedca

\subsection*{Time DowntimeStarts}

\subsection*{Time DowntimeEnds}

\subsection*{std::string Staging}

ARC0: nordugrid-cluster-nodeaccess

\subsection*{std::string Jobdescription}

\section{ComputingService and ComputingShare load attributes}

\subsection*{int TotalJobs}

ARC0: nordugrid-cluster-totaljobs \\
CREAM: GlueCEStateTotalJobs (GlueVOView $||$ GlueCE)

\subsection*{int RunningJobs}

ARC0: nordugrid-queue-running \\
CREAM: GlueCEStateRunningJobs (GlueVOView $||$ GlueCE)

\subsection*{int WaitingJobs}

ARC0: nordugrid-queue-queued $||$ nordugrid-cluster-queuedjobs \\
CREAM: GlueCEStateWaitingJobs (GlueVOView $||$ GlueCE)

\subsection*{int StagingJobs}

\subsection*{int SuspendedJobs}

\subsection*{int PreLRMSWaitingJobs}

ARC0: nordugrid-queue-prelrmsqueued

\subsection*{int LocalRunningJobs}

ARC0: nordugrid-queue-running $-$ nordugrid-queue-gridrunning

\subsection*{int LocalWaitingJobs}

ARC0: nordugrid-queue-queued $-$ nordugrid-queue-gridqueue

\subsection*{int FreeSlots}

CREAM: GlueCEStateFreeJobSlots $||$ GlueCEStateFreeCPUs (GlueVOView $||$ GlueCE)

\subsection*{std::string FreeSlotsWithDuration}

\subsection*{int UsedSlots}

ARC0: nordugrid-queue-usedcpus

\subsection*{int RequestedSlots}

\section{ComputingShare attributes}

\subsection*{std::string MappingQueue}

ARC0: nordugrid-queue-name

\subsection*{Period MaxWallTime}

ARC0: nordugrid-queue-maxwalltime \\
CREAM: GlueCEPolicyMaxWallClockTime (GlueVOView $||$ GlueCE)

\subsection*{Period MaxTotalWallTime}

\subsection*{Period MinWallTime}

ARC0: nordugrid-queue-minwalltime

\subsection*{Period DefaultWallTime}

ARC0: nordugrid-queue-defaultwalltime

\subsection*{Period MaxCPUTime}

ARC0: nordugrid-queue-maxcputime \\
CREAM: GlueCEPolicyMaxCPUTime (GlueVOView $||$ GlueCE)

\subsection*{Period MaxTotalCPUTime}

\subsection*{Period MinCPUTime}

ARC0: nordugrid-queue-defaultcputime

\subsection*{Period DefaultCPUTime}

ARC0: nordugrid-queue-defaultcputime

\subsection*{int MaxTotalJobs}

CREAM: GlueCEPolicyMaxTotalJobs (GlueVOView $||$ GlueCE)

\subsection*{int MaxRunningJobs}

ARC0: nordugrid-queue-maxrunning \\
CREAM: GlueCEPolicyMaxRunningJobs (GlueVOView $||$ GlueCE)

\subsection*{int MaxWaitingJobs}

ARC0: nordugrid-queue-maxqueable \\
CREAM: GlueCEPolicyMaxWaitingJobs (GlueVOView $||$ GlueCE)

\subsection*{int NodeMemory}

ARC0: nordugrid-queue-nodememory $||$ nordugrid-cluster-nodememory \\
CREAM: GlueHostMainMemoryRAMSize

\subsection*{int MaxPreLRMSWaitingJobs}

\subsection*{int MaxUserRunningJobs}

ARC0: nordugrid-queue-maxuserrun \\
CREAM: GlueCEPolicyAssignedJobSlots (GlueVOView $||$ GlueCE) % ??

\subsection*{int MaxSlotsPerJob}

CREAM: GlueCEPolicyMaxSlotsPerJob (GlueVOView $||$ GlueCE)

\subsection*{int MaxStageInStreams}
\subsection*{int MaxStageOutStreams}
\subsection*{std::string SchedulingPolicy}

ARC0: nordugrid-queue-schedulingpolicy

\subsection*{int MaxMemory}

ARC0: nordugrid-queue-nodememory $||$ nordugrid-cluster-nodememory \\
CREAM: GlueHostMainMemoryVirtualSize

\subsection*{int MaxDiskSpace}
\subsection*{URL DefaultStorageService}

ARC0: nordugrid-cluster-localse \\
CREAM: GlueCEInfoDefaultSE (GlueVOView $||$ GlueCE)

\subsection*{bool Preemption}

CREAM: GlueCEPolicyPreemption (GlueVOView $||$ GlueCE)

\subsection*{Period EstimatedAverageWaitingTime}

CREAM: GlueCEStateEstimatedResponseTime (GlueVOView $||$ GlueCE)

\subsection*{Period EstimatedWorstWaitingTime}

CREAM: GlueCEStateWorstResponseTime (GlueVOView $||$ GlueCE)

\subsection*{std::string ReservationPolicy}

\section{ComputingManager attributes}

\subsection*{std::string ManagerType}

ARC0: nordugrid-cluster-lrms-type (nordugrid-cluster-lrms-version)

\subsection*{bool Reservation}
\subsection*{bool BulkSubmission}
\subsection*{int TotalPhysicalCPUs}

ARC0: nordugrid-queue-totalcpus $||$ nordugrid-cluster-totalcpus

\subsection*{int TotalLogicalCPUs}

ARC0: nordugrid-queue-totalcpus $||$ nordugrid-cluster-totalcpus

\subsection*{int TotalSlots}

ARC0: nordugrid-queue-totalcpus $||$ nordugrid-cluster-totalcpus

\subsection*{bool Homogeneity}

ARC0: nordugrid-queue-homogeneity $||$ nordugrid-cluster-homogeneity

\subsection*{std::string NetworkInfo}

\subsection*{bool WorkingAreaShared}

\subsection*{int WorkingAreaFree}

ARC0: nordugrid-cluster-sessiondir-free

\subsection*{Period WorkingAreaLifeTime}

ARC0: nordugrid-cluster-sessiondir-lifetime

\subsection*{int CacheFree}

ARC0: nordugrid-cluster-cache-free

\section{ExecutionEnvironment attributes}

\subsection*{std::string Platform}

ARC0: nordugrid-queue-architecture $||$ nordugrid-cluster-architecture

\subsection*{bool VirtualMachine}

\subsection*{std::string CPUVendor}

ARC0: nordugrid-queue-nodecpu $||$ nordugrid-cluster-nodecpu

\subsection*{std::string CPUModel}

ARC0: nordugrid-queue-nodecpu $||$ nordugrid-cluster-nodecpu

\subsection*{std::string CPUVersion}

ARC0: nordugrid-queue-nodecpu $||$ nordugrid-cluster-nodecpu

\subsection*{int CPUClockSpeed}

\subsection*{int MainMemorySize}

\subsection*{std::string OSFamily}

ARC0: nordugrid-queue-opsys $||$ nordugrid-cluster-opsys

\subsection*{std::string OSName}

ARC0: nordugrid-queue-opsys $||$ nordugrid-cluster-opsys

\subsection*{std::string OSVersion}

\subsection*{bool ConnectivityIn}

\subsection*{bool ConnectivityOut}

\subsection*{std::list<Benchmark> Benchmarks}

ARC0: nordugrid-queue-benchmark $||$ nordugrid-cluster-benchmark

\section{ApplicationEnvironment}

\subsection*{std::list<ApplicationEnvironment> ApplicationEnvironments}

ARC0: nordugrid-cluster-runtimeenvironment \\
CREAM: GlueHostApplicationSoftwareRunTimeEnvironment

\chapter{{\Job}}
\label{app:job}

\section{Information stored in the job list file}

\subsection*{std::string Flavour}

\subsection*{URL JobID}

\subsection*{URL Cluster}

\subsection*{URL SubmissionEndpoint}

\subsection*{URL InfoEndpoint}

\subsection*{URL ISB}

\subsection*{URL OSB}

\subsection*{URL AuxURL}

\subsection*{std::string AuxInfo}

\section{Information retrieved from the informtaion system}

\subsection*{std::string Name}

ARC0: nordugrid-job-jobname

\subsection*{std::string Type}

\subsection*{URL IDFromEndpoint}

\subsection*{std::string LocalIdFromManager}

\subsection*{std::string JobDescription}

\subsection*{std::string State}

ARC0: nordugrid-job-status

\subsection*{std::string RestartState}

ARC0: nordugrid-job-rerunable

\subsection*{int ExitCode}

ARC0: nordugrid-job-exitcode

\subsection*{std::string ComputingManagerExitCode}

\subsection*{std::list<std::string> Error}

ARC0: nordugrid-job-errors

\subsection*{int WaitingPosition}

ARC0: nordugrid-job-queuerank

\subsection*{std::string UserDomain}

\subsection*{std::string Owner}

ARC0: nordugrid-job-globalowner

\subsection*{std::string LocalOwner}

\subsection*{Period RequestedWallTime}

ARC0: nordugrid-job-reqwalltime

\subsection*{Period RequestedTotalCPUTime}

ARC0: nordugrid-job-reqcputime

\subsection*{int RequestedMainMemory}

\subsection*{int RequestedSlots}

\subsection*{std::string StdIn}

ARC0: nordugrid-job-stdin

\subsection*{std::string StdOut}

ARC0: nordugrid-job-stdout

\subsection*{std::string StdErr}

ARC0: nordugrid-job-stderr

\subsection*{std::string LogDir}

ARC0: nordugrid-job-gmlog

\subsection*{std::list<std::string> ExecutionNode}

Arc0: nordugrid-job-executionnodes

\subsection*{std::string ExecutionCE}

ARC0: nordugrid-job-execcluster

\subsection*{std::string Queue}

ARC0: nordugrid-job-execqueue

\subsection*{Period UsedWallTime}

ARC0: nordugrid-job-usedwalltime

\subsection*{Period UsedTotalCPUTime}

ARC0: nordugrid-job-usedcputime

\subsection*{int UsedMainMemory}

ARC0: nordugrid-job-usedmem

\subsection*{std::list<std::string> UsedApplicationEnvironment}

ARC0: nordugrid-job-runtimeenvironment

\subsection*{int UsedSlots}

ARC0: nordugrid-job-cpucount

\subsection*{Time LocalSubmissionTime}

\subsection*{Time SubmissionTime}

ARC0: nordugrid-job-submissiontime

\subsection*{Time ComputingManagerSubmissionTime}

\subsection*{Time StartTime}

\subsection*{Time ComputingManagerEndTime}

\subsection*{Time EndTime}

ARC0: nordugrid-job-completiontime

\subsection*{Time WorkingAreaEraseTime}

ARC0: nordugrid-job-sessiondirerasetime

\subsection*{Time ProxyExpirationTime}

ARC0: nordugrid-job-proxyexpirationtime

\subsection*{std::string SubmissionHost}

ARC0: nordugrid-job-submissionui

\subsection*{std::string SubmissionClientName}

ARC0: nordugrid-job-clientsoftware

\subsection*{Time CreationTime}

ARC0: Mds-validfrom

\subsection*{Period Validity}

ARC0: Mds-validto $-$ Mds-validfrom

\subsection*{std::string OtherMessages}

ARC0: nordugrid-job-comment

\section{Associations}

\subsection*{URL JobManagementEndpoint}

\subsection*{URL DataStagingEndpoint}

\section{ExecutionEnvironment (condensed)}

\subsection*{bool VirtualMachine}

\subsection*{std::string UsedCPUType}

\subsection*{std::string UsedOSFamily}

\subsection*{std::string UsedPlatform}
